\documentclass{two-column-resume}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}

\begin{document}
    \name{Michael}{Meding}
    \contact{\href{mailto:mike@mikemeding.com}{mike@mikemeding.com} | +1 (214) 334-1905 | \href{www.mikemeding.com}{www.mikemeding.com}}
    \headerline
    \noindent
    \begin{minipage}[t]{0.33\textwidth}
        \vspace{0.5\baselineskip}


        %============================ EDUCATION ========================================
        \section{Education}
        \shortitem{Masters \tiny{Computer Science}}
        \itemdetails{
        \footnotesize{University of Massachusetts Lowell} \\
        \footnotesize{May 2016}
        }

        \shortitem{Bachelors \tiny{Computer Science}}
        \itemdetails{
        \footnotesize{University of Massachusetts Lowell} \\
        \footnotesize{May 2015 \tiny{(With Honors)}}
        }

        %============================ LANGUAGE PROFICIENCIES ========================================
        \section{Proficiencies}
        \shortitem{Languages}
        \itemdetails{
        Python 2 \& 3 $\bullet\bullet\bullet\bullet\bullet$\\
        JavaScript $\bullet\bullet\bullet\bullet\bullet$\\
        Java 7 \& 8 $\bullet\bullet\bullet\bullet\bullet$\\
        C/C++ $\bullet\bullet\bullet\bullet\circ$\\%
%        Firmware C (Atmel+Microchip)\\
        Linux Bash $\bullet\bullet\bullet\bullet\bullet$\\%
        Assembly $\bullet\bullet\bullet\circ\circ$\\%
        \LaTeX $\space\bullet\bullet\bullet\bullet\circ$\\
        }

        %============================ DATABASES ========================================
        \shortitem{Databases}
        \itemdetails{
        MySQL $\bullet\bullet\bullet\bullet\bullet$\\%
        InfluxDB $\bullet\bullet\bullet\bullet\circ$\\%
        MongoDB $\bullet\bullet\bullet\bullet\circ$\\%
        Neo4j $\bullet\bullet\bullet\circ\circ$\\%
        }

        %============================ WEB TECHNOLOGIES ========================================
        \shortitem{Web Technologies}
        \itemdetails{
        AngularJS $\bullet\bullet\bullet\bullet\bullet$\\%
        ReactJS $\bullet\bullet\bullet\bullet\bullet$\\%
        Redux $\bullet\bullet\bullet\bullet\bullet$\\%
        Twitter Bootstrap $\bullet\bullet\bullet\bullet\bullet$\\%
        D3 $\bullet\bullet\bullet\bullet\bullet$\\%
        HTML5 $\bullet\bullet\bullet\bullet\circ$\\%
        jQuery $\bullet\bullet\bullet\bullet\circ$\\%
        CSS3 $\bullet\bullet\bullet\bullet\circ$\\%
        Sass $\bullet\bullet\bullet\bullet\circ$\\%
        SVG $\bullet\bullet\bullet\circ\circ$\\%
        }

        \shortitem{Other}
        \itemdetails{
        Solidworks $\bullet\bullet\bullet\bullet\circ$\\%
        ROS $\bullet\bullet\bullet\circ\circ$\\
        (Robot Operating System) \\
        }


    \end{minipage}% This hacky percent sign is for removing the space between two columns.
    \begin{minipage}[t]{0.67\textwidth}
        \vspace{0.5\baselineskip}


        %============================ EXPERIENCE ========================================
        \section{Experience}
        % ZEA
        \longitem{Lead Software Developer}{}{Zea Biosciences}{Sep 2018 - Present}
        \itemdetails{
        \begin{itemize}[itemsep=0pt]
            \item Created an intelligent plant growth and facilities management system.
            The system is a 3-tier SPA design using Django and ReactJS technologies.
            \item Integrated existing systems data into an InfluxDB time series database for live plant condition analysis.
            \item Handled all linux systems administration and software deployment.
        \end{itemize}
        }
        % EFACTO
        \longitem{Senior Software Developer}{}{Efacto Power}{Jan 2017 - Aug 2018}
        \itemdetails{
        \begin{itemize}[itemsep=0pt]
            \item Designed a cloud-based big data time series for storing and analyzing patterns in energy.
            This design leveraged the power of Hadoop and the OpenTSDB framework.
            \item Managing product development and production of the IoT gateways and sensors.
            This involved all aspects of the manufacturing processes from product development to production.
        \end{itemize}
        }
        % OUTSMART
        \longitem{Software Developer}{}{Outsmart Power Systems}{Aug 2015 - Dec 2016}
        \itemdetails{
        \begin{itemize}[itemsep=0pt]
            \item Created a content management system for maintaining business related customer data on the web.
            This included responsive web design elements for both mobile and desktop using AngularJS.
            \item Built a websocket-based IoT communication platform using Java.
            \item Designed responsive D3 charts for in depth analysis of data collected from IoT sensors.
        \end{itemize}
        }


        %============================ PROJECTS ========================================
        \section{Projects}
        \longitem{Web Based 3D Slicer}{}{University of Massachusetts Lowell}{2015 - 2016}
        \itemdetails{
        Wrote one of the first 3D print slicers to be deployed to the web.
        This project was also tested on a 3D printer of my own design.
        }
        \longitem{Solidworks Design}{}{Massachusetts Bay Community College}{2015 - Present}
        \itemdetails{
        Studied Mechanical Engineering part time and I have a background designing parts in Solidworks.
        Several of my designs were used in production applications at Efacto Power.
        }

        %        \section{Research}
        %        \longitem{Research Title}{}{Place}{Start Date - End Date}
        %        \itemdetails{
        %        \textit{Styles here are kept.}
        %        }
        %        \section{Awards}
        %        \shortitem{Clean Energy Internship}
        %        \itemdetails{Short items can also be used on the right column.}
        %        \section{Other}
        %        Custom styles can also be used here.
        %        For example, a list of publications using BibTeX.
    \end{minipage}
\end{document}