%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Michael Meding}
\address{(214)~$\cdot$~334~$\cdot$~1905 \\ mikeymeding@gmail.com} 
\address{www.mikemeding.com}
\address{181 Bacon St \\ Natick, Massachusetts 01760}


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Massachusetts Lowell} \hfill {\em May 2016} \\ 
M.S. in Computer Science  \smallskip \\
{\bf University of Massachusetts Lowell} \hfill {\em May 2015} \\ 
B.S. in Computer Science  \smallskip \\
%Overall GPA: 5.678
{\bf Massachusetts Bay Community College} \hfill {\em December 2013} \\ 
A.S. in Computer Science  \smallskip \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

%--------------------------- OUTSCHMART --------------------------------------

\begin{rSubsection}{Outsmart Power Systems}{August 2011 - Present}{Developer}{Natick, MA}
\item Programmed Java EE application framework for interfacing a Neo4j graph database with analytics to the web using EJB3 and RESTful web services.
\item Designed and implemented a content management system for maintaining customer data on the web. This included responsive web design elements for both mobile and desktop using AngularJS and Twitter Bootstrap.
\item Responsible for the deployment of the above web application to respective application and web servers.
\end{rSubsection}

%--------------------------- CRACK ATTACK --------------------------------------

%\begin{rSubsection}{Rack Attack Inc.}{May 2010 - June 2011}{Mechanic and Clerk}{Framingham, MA}
%\item Mechanic and store front clerk at a shop that sells and installs trailer hitches.
%\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	RELEVANT WORK
%----------------------------------------------------------------------------------------
\begin{rSection}{Relevant Work}
% 3D Printing
{\bf Designed custom 3D printer} \hfill {\em Dec 2014 - Current} \\ 
Built an aluminium frame 3D printer from scratch. This printer is now capable of accuracies in the sub 100 micron resolution which is considered exceptional for a home built printer.

% NLP PROJECT
{\bf NLP Twitter Bullying Project} \hfill {\em Sept 2014 - Dec 2014} \\ 
A machine learning and data mining project that learns from a corpus of compiled tweets from Twitter to discover bullies who use social media.

% ODB STUFF
{\bf Arduino ODB2 Protocol Tool} \hfill {\em Sept 2013 - Current} \\ 
A K-line protocol engine diagnostic and logging tool which I have been developing in my spare time using an Arduino and an ECU simulator.  \smallskip \\

\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Java 7 \& 8, Java EE 7, JavaScript, C, C++,  Scheme,\\
 					&  Linux Bash, Assembly, Python 2 \& 3, Misc. Firmware C code, \LaTeX,\\
 					&  ROS (Robot Operating System) \\
Web Technologies & AngularJS , Bootstrap, EmberJS, D3, jQuery, jQueryUI,CSS3,\\
				&  less, Sass, Ajax, HTML 5, SVG \\	
Protocols \& APIs & XML, JSON,  REST, EJB3, JMS, jUnit 3 \& 4 \\
         Databases & MySQL, Derby, Neo4j, MongoDB \\
			 Tools & Git, SVN, Vim, Netbeans, Intellij IDEA, Pycharm, WebStorm, Sublime \\
		 Platforms & Ubuntu (Since Ver 7.04), LinuxMint, CentOS (Since Ver 5.8), Fedora, \\
 & Mac OSX , and Windows \\
\end{tabular}

\end{rSection}

\end{document}
